\papertitle

### 2021-03-10 source_separation/paper/paper.tex
Added NMF section, fixed a broken citation, some grammar

			\subsubsection{Non-negative Matrix Factorization}
			@Max 
			We use scikit learn implementation. Related papers:
			\cite{Cichocki_NMF} \cite{Fevotte_NMF}

			\subsubsection{OpenUnmix}
			Open-Unmix~\cite{open-unmix} is an open source implementation of a deep music source separation model, based on \cite{Uhlich207}. It is actually composed of multiple models that are trained for each target (such as 'vocals', 'drums', ...). Each of these models is trained on the specific target using the same architecture, based on a three layer bidirectionnal LSTM network. Open-Unmix operates on the Short Time Fourier Transform of the input mixture, which is first standardized. It predicts the target by multiplying the output of the LSTM network with the magnitude spectogram of the input, essentially applying a mask. Open-Unmix also use Wiener filtering as a last processing step.

>>>>

			\subsubsection{Non-negative Matrix Factorization} 
			Non-negative matrix factorization \cite{Cichocki_NMF} \cite{Fevotte_NMF} is an \`a priori method, which takes an input non-negative matrix, in this case a spectrogram $S$, in $\mathbb{R} ^{N\times M}$ and decomposes it into a basis matrix $A$ in $\mathbb{R}^{N\times J}$ and a component matrix $X$ in $\mathbb{R}^{J\times M}$ such that $S\approx A\times X$. We use the coordinate descent algorithm from the scikit-learn Python package based on \cite{Cichocki_NMF} with $J$ set to $4$, which selects for 4 features in the dataset. We then output 4 mono waveforms containing each isolated feature $F_i$, where $F_i=A_i\times X_i$ for $i = 1, 2, 3$, or $4$.

			\subsubsection{OpenUnmix}
			Open-Unmix~\cite{open-unmix} is an open source implementation of a deep music source separation model, based on \cite{Uhlich2017}. It is actually composed of multiple models that are trained for each target (such as 'vocals', 'drums', ...). Each of these models is trained on the specific target using the same architecture, based on a three layer bidirectionnal LSTM network. Open-Unmix operates on the Short Time Fourier Transform of the input mixture, which is first standardized. It predicts the target by multiplying the output of the LSTM network with the magnitude spectogram of the input, essentially applying a mask. Open-Unmix also uses Wiener filtering as a last processing step.
